---
title: "Testing PNMF"
author: "Richard Beare"
date: "22/09/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk("pnmf_face_trials.R")
```

# Trials of the various PNMF functions

Idea is to test out the various initialization/seeding options and confirm that each 
variation is behaving sensibly. The test set will be a face dataset, as the expected
components are easy to interpret.

Expect the document to take a long time to run.

Note - NMF installed from github:

```{r, eval=FALSE}
devtools::install_github("richardbeare/NMF", ref="ArrayWarning")
```


## Setup

Register the non-core methods (i.e. ones that don't come with NMF) so that they work in the
NMF framework. Load the face data.

```{r Setup}

```

The following NMF tools are available:
```{r Choices}

```


## Check the faces

Select a random 16 faces and display them - prove that they really are faces. Note that there is some inverting
in the plotting commands

```{r RandomFaces}

```
## Run some established methods

ICA and SVD seeds

```{r Brunet, cache=TRUE}

```

Random seeds

```{r BrunetRandomSeed, cache=TRUE}

```

Offset method (Badea, 2009, modification to Lee and Seung)
```{r Offset, cache=TRUE}

```

### Brunet, ICA seed

```{r BrunetPlotICA}

```

### Brunet, nonnegative double singular value decomposition

```{r BrunetPlotNNDSVD}

```

### Brunet, random seed, 20 runs

```{r BrunetPlotRandom}

```

### Offset, ICA seed

```{r OffsetPlotICA}

```

### Offset, nonnegative double singular value decomposition

```{r OffsetPlotNNDSVD}

```

### Brunet, random seed, 20 runs

```{r OffsetPlotRandom}

```


## Projective methods

