---
title: "Testing PNMF"
author: "Richard Beare"
date: "22/09/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk("pnmf_face_trials.R")
```

# Trials of the various PNMF functions

Idea is to test out the various initialization/seeding options and confirm that each 
variation is behaving sensibly. The test set will be a face dataset, as the expected
components are easy to interpret.

Expect the document to take a long time to run.

Note - NMF installed from github:

```{r, eval=FALSE}
devtools::install_github("richardbeare/NMF", ref="ArrayWarning")
```


## Setup

Register the non-core methods (i.e. ones that don't come with NMF) so that they work in the
NMF framework. Load the face data.

```{r Setup}

```

The following NMF tools are available:
```{r Choices}

```


## Check the faces

Select a random 16 faces and display them - prove that they really are faces. Note that there is some inverting
in the plotting commands

```{r RandomFaces}

```
## Run some established methods

ICA and SVD seeds

```{r Brunet, cache=TRUE}

```

Random seeds

```{r BrunetRandomSeed, cache=TRUE}

```

Offset method (Badea, 2009, modification to Lee and Seung)
```{r Offset, cache=TRUE}

```

### Brunet, ICA seed

```{r BrunetPlotICA}

```

### Brunet, nonnegative double singular value decomposition

```{r BrunetPlotNNDSVD}

```

### Brunet, random seed, 20 runs

```{r BrunetPlotRandom}

```

### Offset, ICA seed

```{r OffsetPlotICA}

```

### Offset, nonnegative double singular value decomposition

```{r OffsetPlotNNDSVD}

```

### Offset, random seed, 20 runs

```{r OffsetPlotRandom}

```


## Projective methods

```{r Projective, cache=TRUE}

```

```{r ProjectiveOrtho, cache=TRUE}

```

```{r ProjectiveKL, cache=TRUE}

```
### PNMF plots 

```{r ProjectivePlotICA}

```

```{r ProjectivePlotNNDSVD}

```

```{r ProjectivePlotRandom}

```

### PNMFO plots 

```{r ProjectiveOPlotICA}

```

```{r ProjectiveOPlotNNDSVD}

```

```{r ProjectiveOPlotRandom}

```

### PNMFKL plots 

```{r ProjectiveKLPlotICA}

```

```{r ProjectiveKLPlotNNDSVD}

```

```{r ProjectiveKLPlotRandom}

```

## Summary so far

Classical methods very dependent on seed choice. Some of the results look a bit crap.

We'd like to avoid the random methods - need lots of repeats.

ICA messes up some time.

NNDSVD so far has used the default method, which does not "densify". Test
a couple of the methods with the "average" option. Avoid the "random" option.

## PNMF with average densify
```{r PNMFAveSVD, cache=TRUE}

```
```{r PlotPNMFAveSVD}

```

## Finally - rank selection

Note that I've used a hacked version of NMF to parallelise rank selection. Normally the 
parallel part is within multiple runs, i.e. for random seeding, which we're trying to avoid.

```{r RankSelectPNM}

```

```{r PlotRankPNMFO}

```

```{r PlotRankPNMF}

```

## Face compression

What does the reconstruction look like from 20 components?



